### 2018-06-26 Stickleback_Paper.tex
latest

@@

\todo{Should I put my geography picture here?}

>>>>

\todo{Take out any "we's" and be more specific}

@@

\begin{figure}[htb]
	\begin{center}
  		\includegraphics[width=0.8\linewidth]{GeographyDiagram}
  		\caption{A representation of the geographic and evolutionary history of all populations throughout the simulation. 
		The marine is a one-dimensional, continuous population with spatial positions ranging from [0.0 - 10.0]. Each 
		lake$_{i}$ is a discrete population connected by migration only through the marine at position $i - 0.5$. The introduced lakes 
		have the same location and selective pressure as the original lakes, but arise at 40K generations, 
		initialized as a copy of all marine individuals.}
  		\label{fig:Geo}
	\end{center}
\end{figure}
